Nextstrain: real-time tracking of pathogen evolution

### 2018-04-18 whitepaper.tex
Small fix

Maximum likelihood ancestral state reconstruction of discrete traits such as country or region of isolation allows identification of probable transmission events given the sampled data, together with inferred probability distribution of ancestral state at each node.
Internal node colours indicate ancestral state and shifts in ancestral state are drawn as links between demes on the map.
It is important to make known the uncertainty of such reconstructions.
Confidence is conveyed by matching colour saturation to the confidence of that trait, and by displaying all relevant information when one hovers over the corresponding branch or isolate on the tree.
Sampling bias and lack of data can obscure transmission links, and in certain cases we have chosen not to display the inferred states.

>>>>

Maximum likelihood ancestral state reconstruction of discrete traits such as country or region of isolation allows identification of probable transmission events given the sampled data, together with inferred probability distributions of ancestral state at each node.
Internal node colours indicate ancestral state and shifts in ancestral state are drawn as links between demes on the map.
Confidence is conveyed by matching colour saturation to the confidence of that trait, and by displaying all relevant information when one hovers over the corresponding branch or isolate on the tree.
Sampling bias and lack of data can obscure transmission links, and in certain cases we have chosen not to display the inferred states.
